### 2014-12-10 inst/vign/taxize_vignette.Rmd
udpated vignette

@@

********************

## Quick start

### Installation

@@

### Resolve taxonomic name

@@

```{r resolvenames, eval=TRUE, cache=FALSE}
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
temp$results[ , -c(1,4)]
```

@@

### Retrieve higher taxonomic names

@@

#### Interactive name selection
As mentioned most databases use a numeric code to reference a species. A general workflow in taxize is: Retrieve Code for the queried species and then use this code to query more data/information.

@@

### What taxa are the children of my taxon of interest?

@@

```{r downstream, eval=TRUE, cache=FALSE}
col_downstream(name = "Apis", downto = "Species")
```

The result from the above call to `col_downstream()` is a data.frame that gives a number of columns of different information.

### Matching species tables with different taxonomic resolution

>>>>

```{r, eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE
)
```

@@

## Installation

@@

## Resolve taxonomic name

@@

```{r resolvenames, eval=TRUE, cache=FALSE}
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
head( temp$results )
```

@@

## Retrieve higher taxonomic names

@@

## Interactive name selection

As mentioned most databases use a numeric code to reference a species. A general workflow in taxize is: Retrieve Code for the queried species and then use this code to query more data/information.

@@

There are functions for many other sources

* `get_boldid()`
* `get_colid()`
* `get_eolid()`
* `get_gbifid()`
* `get_nbnid()`
* `get_tpsid()`
* `get_ubioid()`

Sometimes with these functions you get a lot of data back. In these cases you may want to limit your choices. Soon we will incorporate the ability to filter using `regex` to limit matches, but for now, we have a new parameter, `rows`, which lets you select certain rows. For example, you can select the first row of each given name, which means there is no interactive component:

```{r}
get_nbnid(c("Zootoca vivipara","Pinus contorta"), rows = 1)
```

Or you can select a range of rows

```{r}
get_nbnid(c("Zootoca vivipara","Pinus contorta"), rows = 1:3)
```

In addition, in case you don't want to do interactive name selection in the case where there are a lot of names, you can get all data back with functions of the form, e.g., `get_tsn_()`, and likewise for other data sources. For example:

```{r}
out <- get_nbnid_("Poa annua")
NROW(out)
```

That's a lot of data, so we can get only certain rows back

```{r}
get_nbnid_("Poa annua", rows = 1:10)
```

## Coerce numerics/alphanumerics to taxon IDs

We've also introduced in `v0.5` the ability to coerce numerics and alphanumerics to taxonomic ID classes that are usually only retrieved via `get_*()` functions.

For example, adfafd

```{r}
as.gbifid(get_gbifid("Poa annua")) # already a uid, returns the same
as.gbifid(2704179) # numeric
as.gbifid("2704179") # character
as.gbifid(list("2704179","2435099","3171445")) # list, either numeric or character
```

These `as.*()` functions do a quick check of the web resource to make sure it's a real ID. However, you can turn this check off, making this coercion much faster:

```{r}
system.time( replicate(3, as.gbifid(c("2704179","2435099","3171445"), check=TRUE)) )
system.time( replicate(3, as.gbifid(c("2704179","2435099","3171445"), check=FALSE)) )
```

## What taxa are downstream of my taxon of interest?

@@

```{r downstream1, eval=TRUE, cache=FALSE}
downstream("Apis", downto = "Species", db = "col")
```

We can also request data from ITIS

```{r downstream2, eval=TRUE, cache=FALSE}
downstream("Apis", downto = "Species", db = "itis")
```

## Direct children

You may sometimes only want the direct children. We got you covered on that front, with methods for ITIS, NCBI, and Catalogue of Life. For example, let's get direct children (species in this case) of the bee genus _Apis_ using COL data:

```{r}
children(get_colid("Apis"))
```

The direct children (genera in this case) of _Pinaceae_ using NCBI data:

```{r}
children("Pinaceae", db = "ncbi")
```

## Get NCBI ID from GenBank Ids

With accession numbers

```{r}
genbank2uid(id = 'AJ748748')
```

With gi numbers

```{r}
genbank2uid(id = 62689767)
```

## Matching species tables with different taxonomic resolution
